# R Exercises

**Sequences of Numbers, Vectors**

- Generate x=3 6 8
- Calculate $x/2$, $x^2$, $\sqrt{x}$.
- Display the second element of $x$ 
- Create a vector with the first and the third element of $x$.
- Remove the third elmement from $x$.
- Generate y= 2 5 1
- Calculate $x-y$, $x*y$ and x'%*%y and x%*%y'.
- Display elements of x, for which y is larger than 1.5.
- Element(s) of y for which the element in x is equal to 6.
- Generate a vector of integers from 4-10.
- Using seq and rep, (a) generate a vector ranging from 2-3 in 0.1 steps, (b) generate a vector that repeats the elements of $x$ 4 times, i.e. the first four elements of the new vector are four times the first element of $x$, etc.

```{r, error=TRUE,eval=F}

x <- c(3,6,8)
x
x/2
x^2
sqrt(x)
x[2]
x[c(1,3)]
x[-3]
y <- c(2,5,1)
y
x-y
x*y
t(x)%*%y
(x)%*%t(y)
x[1]*y[1]+x[2]*y[2]+x[3]*y[3]
x[y>1.5]###Elements of x, for which y is larger than 1.5
y[x==6]##Element of y for which the element in x is equal to 6.
4:10 ##
seq(2,3,by=0.1)
rep(x,each=4)

```


## Matrices



- Generate a matrix 

$$A=\left(\begin{matrix}
    1&    2 &   5\\
    4   & 7 &   3
\end{matrix}\right)$$
- Check the dimensions of A.
- Generate a matrix 
$$B=\left(\begin{matrix}
    1&    4 &   2\\
    7   & 5 &   3
\end{matrix}\right)$$

- Check the dimensions of B.
- Generate a square matrix C:
$$A=\left(\begin{matrix}
    1&    -1 \\
    -1   & 3 
\end{matrix}\right)$$

- Extract the diagonal elements of C.
- Calculate $(C'C)^{-1}$


```{r, error=TRUE,eval=F}

A <- matrix(c(1,4,2,7,5,3), nrow=2, ncol=3)
A
dim(A)
B <- matrix(c(1,4,2,7,5,3), nrow=2, ncol=3, byrow=T)
B
dim(B)
C<-matrix(c(1,-1,-1,3),nrow=2,ncol=2)
D<-matrix(c(6,3,4,2),nrow=2,ncol=2)
diag(C)
solve(t(C)%*%C)
```

## Sums and frequencies

$$d=(77 \, 93 \, 92\, 68\, 88\, 75\, 100)$$

- Calculate the mean of $d$, i.e $\bar{d}$. 
- Sort all elements of $d$ in ascending/descending order.
- What is the smallest and biggest element of $d$?

```{r, include=F,error=TRUE,eval=F}
d <- c(77, 93, 92, 68, 88, 75, 100)
d
sum(d)
length(d)
mean(d)
sum(d)/length(d)
sort(d)
min(d)
max(d)
```


## Logical Operators

Generate a vector x=c(1:20). Create a vector (each) containing logical operators indicating


- Which elements of x are smaller than 15.
- Which elements of x are smaller than 10 and larger than 5.
- Store the number for which the two statements are true in a vector k. 


```{r, include=F,error=TRUE,eval=F}
x=1:20
z<-x<15
p<-x<10&x>5
k<-c(sum(z),sum(p))
```

## Statistical Distributions

### Exercise 1


Consider this multiple choice test:


- 12 Questions
- 5 possible answers, 1 is correct.



If the answers are chosen randomly


- What is the probability of exactly four correct answers? 
- What is the probability of four or fewer correct answers?

```{r, include=F, error=TRUE,eval=F}

dbinom(4, size=12, prob=0.2) #density function
pbinom(4, size=12, prob=0.2) #cumulative distribution function



```

### Exercise 2

Assume that the results of an exam ($x$ ) are normally distributed with $\mu=72$ and $\sigma=15.2$

- What is the proportion of students that have 84 or more points (on avg.)
- 1000 Students take the exam. Simulate the results, calculate $\bar{x}$ and $\hat{\sigma}$ (with sd()).


```{r, include=T, error=TRUE,eval=T}
pnorm(84, mean=72, sd=15.2, lower.tail=FALSE)
##Oder 
1-pnorm(84, mean=72, sd=15.2, lower.tail=T)
S<-rnorm(1000,72,15.2)
mean(S)
sd(S)


```

### Exercise 3



Generate 1000 random numbers on the interval between a=0 und b=1 with 

$$f(x) =\begin{cases}\frac{1}{b-a} \quad \mbox{if} \quad a\leq x \leq b\\
0 \quad \mbox{if} \quad x<a \quad \mbox{or} \quad x>b \end{cases}$$ 



```{r, include=T, error=TRUE,eval=T}

####Uniform###
set.seed(830)
runif(100, min=0, max=1)
mean(runif(100, min=0, max=1))
```

## Loops and functions


### Exercise 1 

Using the following variables:

- x=1
- y=40
- i=c(1:10)

For this exercise, write a for() loop that increments x by three and decreases y by two, for each i.


```{r, include=F, error=TRUE,eval=F}

##Loops##

x=1
y=40
#i=c(1:10)


for(i in 1:10)
{
  print(x)
  x<-x+3
  y<-y-2
  #print(y)
}
```

### Exercise 2

Using the following variables:

- a=15:10
- b=20:15

For this exercise, type a while () loop that computes a vector x=225 224 221 216 209 200, such that


```{r, include=F, error=TRUE,eval=F}

x[1]=a[1]*b[6]
x[2]=a[2]*b[5]
x[3]=a[3]*b[4]
.
.
x[6]=a[6]*b[1]

```

```{r, include=F, error=TRUE,eval=F}

#########Loops, exercise 2##############
a=15:10
b=20:15
x<-vector(mode = "numeric", length = length(a))
i=0
while(i<length(a))
{
 i=i+1; x[i]<-a[i]*b[length(a)-i+1]
}

```

### Exercise 3 


- Draw a vector $u$ with length 30 from $\mathcal{N}=(0,1)$. 
- Calculate $u^2$ for the first k=10 values in u.
- Calculate $u^2$ for the first k=10 values in u only when $|u|>l=0.8$, otherwise it remains the original value.
- Write a function that takes three arguments ($u,k,l$) and returns two results: A vector of length($k$) with the result of the calculation $u^2$, $u$ respectively) and a scalar indicating the number of elements of $u$ for which the condition is fulfilled. 


```{r, include=T, error=TRUE,eval=T}
# Create a vector filled with random normal values
u1 <- rnorm(30)
print("This loop calculates the square of the first 10 elements of vector u1")
# Initialize `usq`
usq <- 0
for(i in 1:10) {
  # i-th element of `u1` squared into `i`-th position of `usq`
  usq[i] <- u1[i]*u1[i]
  print(usq[i])
}

#u1 <- rnorm(30)
print("This loop calculates the square of the first 10 elements of vector u1 if condition is met")
# Initialize `usq`
usq <- 0
for(i in 1:10) {
  if(abs(u1[i])>0.8){
  # i-th element of `u1` squared into `i`-th position of `usq`
  usq[i] <- u1[i]*u1[i]
  }
  else{
    usq[i]<-u1[i]
  }
  #print(usq[i])
}
print(i)



#u1 <- rnorm(30)
###demonstrating the two different ways to utilize logical operators
u<-u1[1:10]
#z=u[abs(u)>0.8]
z=sum(abs(u)>0.8)
usquared<-function(u,k,l)
{
  print("This loop calculates the square of the first k elements of vector u1, for which u>0.8 ")
  # Initialize `usq`
  usq <- 0
  for(i in 1:k) {
    if(abs(u[i])>l){
      # i-th element of `u1` squared into `i`-th position of `usq`
      usq[i] <- u[i]*u[i]
    }
    else{
      usq[i]<-u[i]
    }
  }
  z=sum(abs(u[1:k])>l)
  return(list(usq=usq,z=z))
}

ergebnis=usquared(u1, 20,0.5)
ergebnis$z
ergebnis$usq
ergebnis


###With the default values###
ergebnis=usquared(u1)
ergebnis

```


